Ceph Parallel File System Evaluation Report

### 2013-11-07 testbed.tex
add testbed

We used Data Direct Networks' (DDN) SFA10K as the storage backend for this
evaluation. SFA10K organizes disks into various RAID levels by two
active-active RAID controllers. Exported RAID groups (LUNs) by these
controllers are driven by four server hosts (oss-[1-4]).  Each server host has
two InfiniBand (IB) QDR connections to the storage backend.  We used a single
dual-port Mellanox ConnectX IB QDR card per host.  By our calculation, this
setup is adequate to drive the SFA10K at its maximum theoretical throughput
(roughly 12 GB/s). 
%Server hosts and SFA10K connection diagram is illustrated in
%Figure~\ref{fig:ddn-sfa10k}.

@@

Our SFA10K system consists of 200 SAS drives and 280 SATA drives, hosted in a
10-tray configuration.
%Each DDN SA4601 disk tray can host up to 60 disks and
%has two SAS links per controller (four in total). The SATA and SAS disks in our
%testbed are distributed evenly over ten SA4601 disk trays (20 SAS and 28 SATA
%disks per tray). 
%Each SFA10K RAID controller has two RAID processors and each
%RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
%groups by the RAID processors (software RAID) and then exported to connected
%server hosts over the IB connections. 
Since each DDN SFA10K controller is a
stand-alone computer system running Linux, CPU and memory affinity while
organizing disks into RAID groups and exporting them is crucial for obtaining
top performance out of an SFA10K system.

@@

Our testing methodology is bottom to top. We start our evaluation from the
lowest level (i.e. block-level)  to establish a baseline performance and work
our way up to the top (i.e. file system-level). We establish an expected
theoretical performance of a given hardware or software layer and then compare
that with the observed results of our experiments. Each added new layer to the
stack introduces new bottlenecks and re-defines the expected theoretical
performance of the overall system. We will explain each component or layer and
its expected performance before we present our observed results.

>>>>

We used a Data Direct Networks (DDN) SFA10K as the storage backend for this
evaluation. SFA10K organizes disks into various RAID levels by two
active-active RAID controllers. In our testbed, exported RAID groups (LUNs) 
are driven by four server hosts (oss-[1-4]).  Each server host has
two InfiniBand (IB) QDR connections to SFA10K.  We used a single
dual-port Mellanox ConnectX IB QDR card per host.  By our calculation, this
setup is adequate to drive the SFA10K at its maximum theoretical throughput
(roughly 12 GB/s). 
%Server hosts and SFA10K connection diagram is illustrated in
%Figure~\ref{fig:ddn-sfa10k}.

@@

Our SFA10K system consists of 200 SAS drives and 280 SATA drives.
% hosted in a
%10-tray configuration. Each DDN SA4601 disk tray can host up to 60 disks and
%has two SAS links per controller (four in total). 
The SATA and SAS disks in our
testbed are distributed evenly over the SFA10K.
%ten SA4601 disk trays (20 SAS and 28 SATA
%disks per tray). 
Each SFA10K controller has two RAID processors and each
RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
groups by the RAID processors and then exported to connected
server hosts.
%over the IB connections. 
%Since each SFA10K controller is a
%stand-alone computer system running Linux, CPU and memory affinity while
%organizing disks into RAID groups and exporting them is crucial for obtaining
%top performance out of an SFA10K system.

@@

Our testing methodology is bottom to top. We start our evaluation from the
block-level to establish a baseline performance and work
our way up to the file system-level. We establish an expected
theoretical performance of a given hardware or software layer and then compare
that with the observed results of our experiments. Each added new layer to the
stack introduces new bottlenecks and re-defines the expected theoretical
performance of the overall system. 
%We will explain each component or layer and
%its expected performance before we present our observed results.
